---
title: "moneyball"
author: "Liu_Boyu"
output: html_document
---


```{r, echo=FALSE}
require(dplyr)
setwd("C:/Users/bl022_000/Desktop/moneyball/MoneyBall/data/2014_2015")

df1 = read.csv("2014_2015_miscellaneous_stats.csv", header = TRUE, encoding="ascii")
df2 = read.csv("2014_2015_opponent_shooting.csv", header = TRUE)
df3 = read.csv("2014_2015_opponent_stats.csv", header = TRUE)
df4 = read.csv("2014_2015_schedule.csv", header = TRUE)
df5 = read.csv("2014_2015_team_shooting.csv", header = TRUE)
df6 = read.csv("2014_2015_team_stats.csv", header = TRUE)
```

# df1 = df1 %>% mutate(Team = ifelse(endsWith(Team,"*"),substr(df1$Team,0,nchar(df1$Team)-1),df1$Team))
# x = "GSW*"
# substr(x,0,nchar(x)-1)
colnames(df1)
colnames(df2)
colnames(df3)
colnames(df4)
colnames(df5)
colnames(df6)

colnames(df2)[colnames(df2)!="Team"] <- paste("oppo", colnames(df2)[colnames(df2)!="Team"], sep = "_")
colnames(df3)[colnames(df3)!="Team"] <- paste("oppo", colnames(df3)[colnames(df3)!="Team"], sep = "_")

df1 = df1[-c(1)]
df2 = df2[-c(1,3,4,5)]
df3 = df3[-c(1,3,4)]
df5 = df5[-c(1,3,4,5)]


```{r}

df = full_join(df1, df2, by="team_name")
df = full_join(df,df3,by="team_name")
df = full_join(df,df5,by="team_name")
df = full_join(df,df6,by="team_name")

clean_end <- function(string){
  if (grepl("[[:punct:]]",string)){
    string = substr(string,0,nchar(string)-1)
  } 
  else {
    string = string
  }
}

df[1] = apply(df[1], 1, clean_end)


write.csv(df, file = "2014_2015_stats.csv")

```

```{r}
setwd("C:/Users/bl022_000/Desktop/moneyball/MoneyBall/data/2015_2016")

df1 = read.csv("2015_2016_miscellaneous_stats.csv", header = TRUE, encoding="ascii")
df2 = read.csv("2015_2016_opponent_shooting.csv", header = TRUE)
df3 = read.csv("2015_2016_opponent_stats.csv", header = TRUE)
df4 = read.csv("2015_2016_schedule.csv", header = TRUE)
df5 = read.csv("2015_2016_team_shooting.csv", header = TRUE)
df6 = read.csv("2015_2016_team_stats.csv", header = TRUE)

```

colnames(df2)[colnames(df2)!="Team"] <- paste("oppo", colnames(df2)[colnames(df2)!="Team"], sep = "_")
colnames(df3)[colnames(df3)!="Team"] <- paste("oppo", colnames(df3)[colnames(df3)!="Team"], sep = "_")

df1 = df1[-c(1)]
df2 = df2[-c(1,3,4,5)]
df3 = df3[-c(1,3,4)]
df5 = df5[-c(1,3,4,5)]

```{r}
df = full_join(df1, df2, by="team_name")
df = full_join(df,df3,by="team_name")
df = full_join(df,df5,by="team_name")
df = full_join(df,df6,by="team_name")

# df[1] = apply(df[1], 1, clean_end)

write.csv(df, file = "2015_2016_stats.csv")
```







